---
title: "Bioinformatics I Exercises"
---

---------------------------------

# Introduction

All exercises for the lecture Bioinformatics I are provided on this web page.

The exercises complement the lecture and aim to improve your understanding of the diverse topics of this course.

:::: {#explaining .message-box }

::: {#note-exp .note-header}
```{r, include=knitr::is_html_output(), echo=FALSE,}
knitr::include_graphics("figures/infoicon.svg")
```
**Note**
:::
::: {#note-exp .note-body}


We highly recommend doing these exercises. It will help you to prepare for the 
exam.

:::


::::

# Details

Exercises contain two parts:

- theory and calculation questions 
- programming assignments.

Theory and calculation questions can be found on this web page.

Programming assignments are available via Github Classroom. Links to the programming assignments will be provided in the corresponding exercise sheet.
Not every exercise sheet will have a programming assignment.

Exercises are designed for self-teaching. Every week there will be an exercise session where questions about the current exercise sheet will be answered and discussed. Please check the Bioinformatics I Ilias course page for more information about dates and times.

:::: {#explaining .warning-box }

::: {#note-exp .warning-header}
```{r, include=knitr::is_html_output(), echo=FALSE,}
knitr::include_graphics("figures/warningicon.svg")
```
**Warning**
:::
::: {#note-exp .note-body}

You will find hints in the self learning materials which e.g. include information
about the formulae that you have to use.
However, in the exam we won't provide those formulae. You have to learn them by heart.

:::


::::


```{r, include=knitr::is_html_output(), echo=FALSE,}
knitr::asis_output('<div id="admin-panel"><a href="admin.html" class="fill-div"></a></div>')
```


